### 2014-03-07 src/methodology.Rnw
selective mutation

For operator reduction, we utilized the constrained mutation operators suggested by Wong et al.~\cite{wong1995reducing}, Offutt et al.~\cite{offutt1996anexperimental,deng2013empirical}, % TODO Barbosa
 and, Namin et al~\cite{siami2008sufficient}. Since Javalanche~\cite{javalanche} utilized operator selection mechanisms, we also compared the Javalanche operators for operator selection.

>>>>

For selective methods, we tried mutation operators suggested by Wong et al.~\cite{wong1995reducing}, Offutt et al.~\cite{offutt1996anexperimental,deng2013empirical}, % TODO Barbosa
 and, Namin et al~\cite{siami2008sufficient}. Since Javalanche~\cite{javalanche} utilized operator selection mechanisms, we also compared the Javalanche operators for operator selection. Note that all of these techniques except 
Javalanche have targeted C programs, thus some of these operators
are sensible in C but in Java programs. For example C compilers tolerate
removing a return statement but, in Java, it causes a compilation error.
Moreover, there were some operators that are not supported by PIT framework
like ABS (absolute mutation operators), however, we tried to realize as many
as possible operators using PIT's bytecode level mutation. We also extended 
the PIT framework to support the  statement deletion operator (SDL).

{\bf Amin: The rest of this section is for Alex and Carlos info and would be omitted later.}
